A studyforrest extension, an annotation of words and phonemes in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-04-15 paper/main.tex
Fill in URL

In addition, released data, code, and manuscript sources are also available on
Github (\url{https://github.com/psychoinformatics-de/WHAT-EVER}).

>>>>

In addition, released data, code, and manuscript sources are also available on
Github (\url{https://github.com/psychoinformatics-de/studyforrest-paper-speechannotation}).
